%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Modified Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.0 (07/04/2020)
% 
% Author
% Apurv Mishra(https://apurvmishra.xyz)
% Repository
% https://github.com/apurvmishra99/Modified-Deedy-Resume
% Original author of Deedy Resume:
% Debarghya Das (http://debarghyadas.com)
% His repository:
% https://github.com/deedydas/Deedy-Resume
%
%

%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
\usepackage[utf8]{inputenc}
\usepackage{eurosym}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Uppala}{Satya Sai}{ \urlstyle{same}\href{https://satyasai-uppala.github.io/resume}{\bf satysai.me} |
\href{mailto:satyasaiuppala2488@gmail.com}{\bf satyasaiuppala2488@gmail.com} | \bf +91 9390656643| \urlstyle{same}\href{https://github.com/SATYASAI-UPPALA}{\bf Github} |
% \urlstyle{same}\href{https://devpost.com/apurvmishra99}{\bf Devpost} |
\urlstyle{same}\href{https://www.linkedin.com/in/satyasai-uppala-79801a220/}{\bf Linkedin}} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.66\textwidth} 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 
\subsection{SRKR ENGINEERING COLLEGE}
\descript{Bachelor of Engineering (EEE)}
\location{March \textbf{2020} - \textbf{Present} | Bhimavaram, AP}
\textbf{Classification: First Class} (Predicted)
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Ds Redd Consultancy}
\descript{| Project Intern }
\location{Sep \textbf{2021 } – Present | Ideal Lab ,Bhimavaram}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item As an intern to this DST Project, support to work on implemented protocols(CAN) for communication between the charger and vehicle.
\item Developed client applications(web/App).
\item We are implementing the client/server application for ocpp1.6j taken from Github.
\item Worked on Raspberry Pi for an automatic process to the chargers in charging stations.
\end{tightemize}
\sectionsep

\runsubsection{Infitronics Pvt.ltd}
\descript{| SEO Intern }
\location{April  \textbf{2023 } – August {2023} | Hyderabad,Telangana}
\begin{tightemize}
\item Assisted in keyword research and analysis to identify opportunities for website optimization - 80\ \%\.
\item Competitor analysis to identify gaps and opportunities for improvement - 75\%\.
\item  Prepared regular reports on website performance and SEO metrics.
\end{tightemize}
\sectionsep

\runsubsection{CSI(Cyber Security India )}
\descript{| Intern}
\location{3 Months | Remote}
\begin{tightemize}
\item Selected to be a part of Vulnerability analysis after breaking into the top 10 percentile of participants of the CTF challenge.
\item 
 Knowledge learned in the best way possible and making it a moral responsibility to help others around me to develop a safer India !!
\end{tightemize}
\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{EvLocation}
\descript{| Java, XML, APIs, Firabase | \urlstyle{same}\href{https://github.com/SATYASAI-UPPALA}{\bf SourceCode }| \urlstyle{same}\href{https://drive.google.com/file/d/18gvC9tZORhbGnzJkCqF1aKD72J60W4KR/view}{\bf Applink }}
\location{Dec \textbf{2022 }}
\begin{tightemize}
\item Developed an Android application for users to show the availability of charging at a particular station in that locality.
\item Realistic data are taken from IOT to connect the Android 
\item Extracting Apis in ocpp 1.6j and connected to Android application to show the availability.
\end{tightemize}
\sectionsep

\runsubsection{Ar Business Card}
\descript{| C\#\, Unity, Vuforia Engine | \urlstyle{same}\href{https://github.com/SATYASAI-UPPALA/Ar-Visiting-Card.git}{\bf SourceCode }| \urlstyle{same}\href{https://drive.google.com/file/d/1QNrQ-oksORBA_JuJk3izcCXx7uMvf15F/view}{\bf Applink}}
\location{Apr \textbf{2019 }}
\begin{tightemize}
\item From retail to education and gaming, our affordable AR solutions cater to businesses of all sizes.
\item We specialize in customizable AR campaigns that align with your brand identity and target audience.
\item Elevate user experiences with cutting-edge AR technology.
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\end{minipage}%
\hfill
\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{\textbf{Familiar:}}
Python \textbullet{} Java \textbullet{} C\#\\textbullet{}Javascript\textbullet{} \LaTeX\ \\ 
\location{\textbf{Familiar:}}
 \textbullet{Web Technolgies}\textbullet{}Android   \\
 \textbullet{}IOT  \textbullet{Cyber Security}\\
\subsection{OS}
\location{\textbf{Familiar:}}
\textbullet{}Linux \textbullet{}Windows\textbullet{}Kali

\subsection{VCS \& Build Tools}
\textbullet{}Git  \textbullet{} Github Actions
\subsection{Cloud Services}
\location{\textbf{Familiar:}}
\textbullet{}FireBase \textbullet{}MySQL
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 

\textbf{2022 } SIH Runners \\
\textbf{2021 } Acknowledgment for Bounty \\


% \section{Travel \& Conference Grants}

% \textbf{\$250 } ELC, Edinburgh \\
% \textbf{\$250 } PenApps, Philadelphia \\
% \textbf{\textsterling 150 } Algothon, London \\
% \textbf{\texteuro 150 } CEE Hacks, Prague\\
% \textbf{\texteuro 150 } DENEFF EE Hack, Berlin\\
% \textbf{\texteuro 120 } HackUPC, Barcelona\\
% \textbf{\textsterling 75  } Hack Cambridge \\
% \textbf{\texteuro 75    } Junction, Helsinki

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
EV Simulation \\
Burpsuite \\
Matlab Simulation \\

Data Analysis \\
Machine Learning \\
Numerical Computation \\
Tools Development \\
WireShark \\
RPA UI Path\\
Unity Development\\
Algorithms and Data Structures


\section{Activities}
Voultared for FDP in our college. \\
IEEE Member \\
As a member MOU with Hala Mobility \\
Attended Startup Jathara at Anantapur. \\
\section{HOBBIES}
Reding Books\\
Exploring new innovations\\
Playing Cricket, shuttle, Chess\\


\end{minipage}%
\end{document}  
\documentclass[]{article}
